Why Did Russia Fare So Poorly during COVID: An Analysis of Why One of the Best Prepared Countries Could Not Control Excess Deaths

### 2024-02-13 paper/paper.qmd
Added SSRP link. Removed unnecessary files from repo. Updated README.md.

---
title: "Why Did Russia Fare So Poorly during COVID: An Analysis of Why One of the Best Prepared Countries Could Not Control Excess Deaths"
author: 
  - Aryaman Sharma
  - Aviral Bhardwaj
  - Janel Gilani
thanks: "Code and data are available at: https://github.com/Ary4m3n/covid-effect-russia.git; Replication on Social Science Reproduction platform available at: "
date: today
date-format: long
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean tempus libero sit amet nisl dapibus, varius dictum magna pellentesque. In lacinia nec ligula eget condimentum. Aenean imperdiet enim sit amet felis volutpat, eu ornare ante pretium. Donec ullamcorper tempus facilisis. Mauris porttitor libero ultrices tortor facilisis, quis varius sapien ultricies. Pellentesque et metus vel quam mollis dignissim ultricies a dui. Cras sodales porttitor pulvinar. Proin vel nunc sit amet sapien venenatis pellentesque nec at felis."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Why Did Russia Fare So Poorly during COVID: An Analysis of Why One of the Best Prepared Countries Could Not Control Excess Deaths"
author: 
  - Aryaman Sharma
  - Aviral Bhardwaj
  - Janel Gilani
thanks: "Code and data are available at: https://github.com/Ary4m3n/covid-effect-russia.git; Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/8938b287-6681-4a5e-8993-42011a51be58/index"
date: today
date-format: long
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean tempus libero sit amet nisl dapibus, varius dictum magna pellentesque. In lacinia nec ligula eget condimentum. Aenean imperdiet enim sit amet felis volutpat, eu ornare ante pretium. Donec ullamcorper tempus facilisis. Mauris porttitor libero ultrices tortor facilisis, quis varius sapien ultricies. Pellentesque et metus vel quam mollis dignissim ultricies a dui. Cras sodales porttitor pulvinar. Proin vel nunc sit amet sapien venenatis pellentesque nec at felis."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
